Spatial and temporal decay of SARS-CoV-2 environmental contamination of the healthcare environment

### 2021-08-16 manuscript.Rmd
Add interaction model for pandemic duration.

---
title: "Spatial and temporal decay of SARS-CoV-2 environmental contamination of the healthcare environment"
author: "Brendan J. Kelly, MD, MS"
date: "7/19/2021"
output: html_document
---

>>>>

---
#title: "Spatial and temporal effects on SARS-CoV-2 contamination of the healthcare environment"
#author: "Brendan J. Kelly, MD, MS"
output: html_document
---

# Results

### Distance Effect Negligible

### Decay over Time

### Heterogeneity among Subjects in Probability of Detection

### Total Study Day (i.e., Time Into Second Wave) Accounts for Floor Detection Probability

### What Subject-Level Factors Account for Detection Among High-Touch Elevated Sites?
